\documentclass{article}
\usepackage[margin=0.5in]{geometry}
\newenvironment{itquote}
  {\begin{quote}\itshape}
  {\end{quote}\ignorespacesafterend}

\title{Rebuttal - ``Towards Spherical Robots for Mobile Mapping in Human Made Environments''}
\date{\today}

\begin{document}

\maketitle

\paragraph{Reviewer 1}

\begin{itquote}
- Lines 87 and 101: please define "highly precise maps" and "high accuracy".  
\end{itquote}
We added more explanation of ``highly precise'' and ``high accuracy''.

\begin{itquote}
- Line 164: Write out LOAM  
\end{itquote}

We wrote out Lidar odometry and mapping on its first occurrence. 

\begin{itquote}
- Line 168: Delete one "the"  
\end{itquote}

We removed the second occurrence.

\begin{itquote}
- Line 184: Write out RANSAC  
\end{itquote}

We wrote out Random sample consensus on its first occurrence. 

\begin{itquote}
- Line 185: "planes" instead of "places"?  
\end{itquote}

We replaced places with planes.

\begin{itquote}
- Line 551: spelling of sphere  
\end{itquote}

We corrected the spelling of sphere. 

\paragraph{Reviewer 2}

\begin{itquote}
  Line 38 in the clean version: „underground funnel" or „underground tunnel"?
\end{itquote}

We replaced ``funnel'' with ``tunnel''

\begin{itquote}
  Caption of Figure 1, last sentence: Shouldn't it be "3D point projection" instead of "2D point projection"?
\end{itquote}

We replaced ``2D'' with ``3D''

\begin{itquote}
  When referring to equations 3 and 4 in the text within Section 3.3.1. the brackets are missing, which were otherwise used consistently. The same applies with regard to equation 9 in section 3.3.2. Should be checked again throughout.
\end{itquote}

We corrected the references to equations to include the parenthesis. 

\begin{itquote}
  The reference of the variable K in the description of Figure 2 is unclear, as I could not find an introduction to it in advance in the text.
\end{itquote}

We added clarification to the figure caption (number of nearest neighbors). 
Is already introduced before and implied by the AKNN abbreviation. 

\begin{itquote}
 The different colours in Figure 2 probably refer to different segments? This could be added for completeness.
\end{itquote}

We added this information as clarification to the figure caption.

\begin{itquote}
  The use of "figure" or "Figure" is not consistent and should follow the journal's guidelines.
\end{itquote}

We corrected two instances. 
Otherwise we followed the doctrine: Always lower case, unless at the start of a sentence. 



\end{document}
 